---
title: "Climate Normals Report"
author: "Steffi LaZerte"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: journal
    
---

<style>
    body {
        color: #000000;
    }
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, cache = TRUE)
source("00_functions.R")
source("00_header.R")
load("tmp/aquifer_factsheet_data.RData")
load("tmp/aquifer_factsheet_clean_data.RData")
```

## Climate Normals

```{r}
# Original index
climate_index_orig <- read_excel("data/Key_Aquifer_Obs well_EMS ID_climate ID.xlsx", sheet = 1)

# Climate index original
climate_orig <- climate_index_orig %>%
  select(aquifer_id = `Aquifer No`,
         ow = `Obs well`,
         location = Location,
         climate_id_orig = `Climate ID`,
         climate_name_orig = `Nearest climate station`) %>%
  filter(!str_detect(aquifer_id, "(round)|(inactive)")) %>%  # Remove "round 1", etc. from end of file (also NAs)
  mutate(climate_id_orig = as.character(climate_id_orig),
         aquifer_id = as.numeric(aquifer_id))

# Compare to original data
compare <- full_join(climate_orig,
                     ppt_normals %>%
                       select(aquifer_id, ow,
                              climate_name_weathercan = station_name, climate_id_weathercan = climate_id,
                              distance_weathercan = distance, elev_weathercan = elev_climate),
                     by = c("aquifer_id", "ow"))
```

### What changed by using weathercan?

- Originally we had a handmade index that assigned climate ids to observation wells
- Using the weathercan package, we found the best/closest climate station to the observation well and assigned that automatically

```{r}
t <- compare %>%
  summarize(`Total observation wells` = n(),
            `Total OW assigned to climate ID (now)` = sum(!is.na(climate_id_weathercan)),
            `Total OW still unassigned (now)` = sum(is.na(climate_id_weathercan)),
            `OW originally unassigned` = sum(is.na(climate_id_orig)),
            `Added by weathercan method` = sum(is.na(climate_id_orig) & !is.na(climate_id_weathercan)),
            `OW originally assigned` = sum(!is.na(climate_id_orig)),
            `Removed by weather can method` = sum(!is.na(climate_id_orig) & is.na(climate_id_weathercan)))

select(t, 1:3) %>%
  kable(align = "c") %>%
  kableExtra::kable_styling(full_width = FALSE)
```


- Using this method resulting in the addition of many more stations
- But 15 stations were removed (see next section)

```{r}
select(t, 4:7) %>%
  kable(align = "c") %>%
  kableExtra::kable_styling(full_width = FALSE)
```



### Newly missing climate normals

- Which observation wells were assigned a `climate_id` in original file, but don't have one now?
- Why are they missing?
    - **Because they missing an aquifer_id assignment in the GWELLS file OR**
    - **Because they are assigned to a different aquifer_id in the GWELLS than in the original Climate Index (which is correct?)**

**Legend:**

- `ow` = Observation well number
- `aquifer_id_wells` = Aquifer ID associated with the `ow` in the GWELLS database
- `aquifer_id_climate` = Aquifer ID associated with the `ow` in the *original* climate index (i.e. not the new one created by weathercan which uses GWELLS)

```{r}
missing <- filter(compare, !is.na(climate_id_orig) & is.na(climate_id_weathercan)) %>%
  select(aquifer_id, ow, climate_id_orig, climate_name_orig)

wells_db %>%
  select(aquifer_id, ow) %>%
  filter(!is.na(ow)) %>% 
  mutate(aquifer_id = if_else(is.na(aquifer_id), "missing", as.character(aquifer_id))) %>%
  right_join(missing, by = "ow", suffix = c("_wells", "_climate")) %>%
  mutate(problem = case_when(
    aquifer_id_wells == aquifer_id_climate ~
      "No climate station with good data close enough",
    aquifer_id_wells == "missing" ~ "OW is in GWELLS, but is missing an aquifer id",
    aquifer_id_wells != aquifer_id_climate ~
      "OW linked to different aquifer in GWELLS than in original climate index")) %>%
  select(ow, aquifer_id_wells, aquifer_id_climate_orig = aquifer_id_climate, problem) %>%
  arrange(problem) %>%
  DT::datatable(options = list(pageLength = 20, searching = FALSE))
```


## Which stations are far away?

- There are many stations which are > 10 km away from the Observation Well
- Some of these stations may not be the closest station BUT:
    - They are within 15km of the closest station AND
    - They have the best data quality (`code`) withint 15km of the closest station

This table shows all the station options and which stations were chosen.

> **To think about:**
> 
> What is the maximum distance a station should be from an Observation Well?


**Legend**  

- The green/blue rows indicate the chosen station for that observation well
- `data` = Where there climate normals for that station?
- `close` = Was that station within 15km of the closest stations?
- `code` = What is the data calibre of that station? (A = best, D = worst)
- `rank` = Rank 1 was chosen to represent that observation well

```{r}
ppt <- ppt_good %>%
  group_by(aquifer_id, ow) %>%
  mutate(min_dist = min(distance[data]),
         close = distance <= min_dist + 15) %>%
  arrange(aquifer_id, ow, desc(data), desc(close), code) %>%
  mutate(rank = 1:n()) %>%
  mutate(distance = round(distance, 1)) %>%
  select(aquifer_id, ow, station_name, climate_id, distance, data, close, code, rank)

ppt %>%
  filter(aquifer_id %in% aquifer_id[distance[rank == 1] > 10]) %>%
  DT::datatable() %>%
  DT::formatStyle('rank', target = 'row', 
                  backgroundColor = DT::styleEqual(1, '#29af7f50'))
```

## Which stations are SUPER far away?

```{r}
ppt %>%
  mutate(d = distance[rank == 1]) %>%
  filter(aquifer_id %in% aquifer_id[d > 50]) %>%
  arrange(d, rank) %>%
  select(-d) %>%
  DT::datatable(options = list(pageLength = 40, searching = FALSE)) %>%
  DT::formatStyle('rank', target = 'row', 
                  backgroundColor = DT::styleEqual(1, '#29af7f50'))
```
