```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning= FALSE, cache = TRUE)
```


# Comparing new data sources to original data

## Water districts

1. New from `bcmaps::water_districts()` overlaid with aquifers map (from BCDATA online)
2. Original from ????


```{r, cache = TRUE}
source("00_functions.R")
source("00_header.R")
library(kableExtra)
load("tmp/aquifer_factsheet_data.RData")


# GIS - Districts -------------------------------------------------------------

# Original file
water_district <- read_csv("data/Aquifer_Water_District.csv")

# New calculation
wd <- st_intersection(select(bcmaps::water_districts(), water_district = DISTRICT_NAME),
                      select(aquifer_map, aquifer_id)) %>%
  # Calculate area of overlap
  mutate(area = as.numeric(st_area(.))) %>%
  # Calculate dominant water district (max area)
  group_by(aquifer_id) %>%
  mutate(parea = area / sum(area) * 100,
         n = n())

wd_final <- wd %>%
  mutate(extra = if_else(n > 1, paste0(water_district[parea != max(parea)], " (", round(parea[parea != max(parea)], 3), ")", collapse = "; "), as.character(NA))) %>%
  filter(parea == max(parea)) %>%
  select(-area) %>%
  # Remove spatialness
  st_set_geometry(NULL) %>%
  ungroup() %>%
  mutate(aquifer_id = as.numeric(aquifer_id))


p <- full_join(wd_final, rename_all(water_district, tolower),
               by = "aquifer_id", suffix = c("_new", "_orig")) %>%
  filter(water_district_new != water_district_orig |  #where current doesn't match original
           (is.na(water_district_new) & !is.na(water_district_orig))) %>% #where current is missing, but original not
  as.data.frame()
```

```{r eval = FALSE}
# Missing districts

# Are any of the missing district aquifers actually in the aquifers map file? NO!
any(p$aquifer_id[is.na(p$district)] %in% as.numeric(aquifer_map$aquifer_id))

# Because either a) MERGED, b) RETIRED, or c) "469"
filter(aquifer_db_raw, aquifer_id %in% p$aquifer_id[is.na(p$water_district_new)]) %>%
  select(aquifer_id, aquifer_name, location_description)
```


### Potential problems

- Original water district: `water_district_orig`
- New water district: `water_district_new`
- `parea`: Percent overlap between the aquifer polygon and the water_district polygon (New district only)
- `extra`: Shows the percent overlap between the aquifer polygon and a second water_district if it exists.

Here, new water districts have been assigned based on MAXIMUM percent overlap. 


```{r, R.options = list(width = 100)}
# Different districts
filter(p, !is.na(water_district_new) | aquifer_id == 469) %>%
  select(aquifer_id, water_district_orig, water_district_new, parea, extra) %>%
  kable() %>%
  kable_styling()
```


**Some of the orig water districts seem definitely wrong**

- 382 only has 8.7% overlap with Cariboo water district, but has 91.3% overlap with Quesnel water district, why was Cariboo selected in the original data? Mistake?

**Some seem ambiguous**

- 45 and 49 each have about 50-50 split between Vancouver and New Westminister water districts

**Some are unknown**

- 469 is not in the aquifer map, why not?


> **SUGGESTION:**  
>
> - Use 'Vernon' for aquifer 469
> - Take the water district with the highest overlap with our aquifer **OR**
> - Use hybrid districts (similar to regions, below), such as "Vancouver and New Westminister", when there is no district with at least 95% overlap


## Regions

1. New from `bcmaps::nr_regions()` overlaid with aquifers map (from BCDATA online)
2. Original from ????

```{r, cache = TRUE}
# GIS - Regions -----------------------------------------------------------
# Manual GIS analysis?
aquifer_loc_region <- read_csv("data/Aquifer Location Description and Regions.csv")

temp <- select(bcmaps::nr_regions(), region = REGION_NAME) %>%
  mutate(region = str_remove(region, " Natural Resource Region"),
         region = str_remove(region, "-Boundary")) %>%
  st_intersection(select(aquifer_map, aquifer_id)) %>%
  mutate(area = as.numeric(st_area(.))) %>%
  group_by(aquifer_id) %>%
  mutate(parea = area / sum(area) * 100,
         n = n(),
         region = if_else(n > 1 & all(parea < 95), paste0(region, collapse = " and "), region)) %>%
  filter(parea == max(parea)) %>%
  ungroup() %>%
  st_set_geometry(NULL)

p <- aquifer_loc_region %>%
  rename_all(tolower) %>%
  select(aquifer_id, region) %>%
  mutate(region = str_replace_all(region, c("Thomson" = "Thompson",
                                            "  " = " ",
                                            "cC" = "C",
                                            "kootenay" = "Kootenay",
                                            "&" = "and"))) %>%
  full_join(select(temp, aquifer_id, region, parea),
            by = "aquifer_id", suffix = c("_orig", "_new")) %>%
  mutate(region_new = str_remove(region_new, "-Boundary")) %>%
  filter(region_orig != region_new | (parea > 80 & parea < 100))
```

Here, new regions have been assigned based on the criteria apparent in the original regional designations:

- Single region where > 95% overlap
- Hybrid regions where < 95% overlap

For example, aquifer 809 overlaps both Kooteny and Thompson-Okanagan, so is called "Kootenay and Thompson-Okanagan" (this matches the original regional designation).

```{r}
filter(p, aquifer_id == 809) %>% select(-region_orig) %>% kable()%>%
  kable_styling()
```

### Potential problems

- Original region: `region_orig`
- New region: `region_new`
- `parea`: Percent overlap between the aquifer polygon and the region polygon (New region only)

```{r}
filter(p, region_orig != region_new) %>% mutate(parea = as.character(round(parea, 3))) %>% kable()%>%
  kable_styling()
```

- 322: Seems like such a tiny overlap with Thompson-Okanagan should be ignored
- Other small overlaps are ignored:

```{r}
filter(p, region_orig == region_new) %>% mutate(parea = as.character(round(parea, 3))) %>% kable()%>%
  kable_styling()
```

```{r}
lims <- st_bbox(filter(aquifer_map, aquifer_id %in% c(322)))

ggplot(data = filter(bcmaps::nr_regions(), str_detect(REGION_NAME, "South Coast|Thompson-Okanagan"))) +
  geom_sf() +
  geom_sf_label(aes(label = str_extract(REGION_NAME, "South Coast|Thompson-Okanagan"))) +
  geom_sf(data = filter(aquifer_map, aquifer_id %in% c(322)),
          colour = "red") +
  labs(title = "South Coast and Thompson-Okanagan (red is 322)")

ggplot(data = filter(bcmaps::nr_regions(), str_detect(REGION_NAME, "South Coast|Thompson-Okanagan"))) +
  geom_sf(aes(fill = str_extract(REGION_NAME, "South Coast|Thompson-Okanagan"))) +
  scale_fill_manual(name = "Region", values = c("grey50", "grey20")) +
  geom_sf(data = filter(aquifer_map, aquifer_id %in% c(322)),
          fill = "red", size = 3, colour = "black", alpha = 0.3) +
  geom_sf_label(data = filter(aquifer_map, aquifer_id %in% c(322)),
                aes(label = aquifer_id), hjust = 1) +
  coord_sf(xlim = lims[c(1, 3)] + c(-2000, 2000),
           ylim = lims[c(2, 4)] + c(-2000, 2000)) +
  labs(title = "Close up (322 doesn't overlap with Thompson-Okanagan")
```

- 1040 and 1041: Either incorrectly located in the aquifer map or were incorrectly labeled in the original regions
- Based on the map images we have for these aquifers, I think the original regional designation was incorrect
```{r, echo = FALSE}
# Should Kootenay be Kootenay-Boundary?
ggplot(data = filter(bcmaps::nr_regions(), str_detect(REGION_NAME, "Omineca|Northeast"))) +
  geom_sf() +
  geom_sf_label(aes(label = str_extract(REGION_NAME, "Omineca|Northeast"))) +
  geom_sf(data = filter(aquifer_map, aquifer_id %in% c(1040, 1041)),
          colour = "red") +
  labs(title = "Aquifers 1040 and 1041 (in red)")

ggplot(data = filter(aquifer_map, aquifer_id %in% c(1040, 1041))) +
  geom_sf(colour = "red") +
  geom_sf_label(data = filter(aquifer_map, aquifer_id %in% c(1040, 1041)),
                aes(label = aquifer_id), hjust = 1, vjust = c(-0.5, 0.5)) +
  labs(title = "Close up")
```

> **SUGGESTIONS**
>
> - Ignore all mismatches and use the new region assigned

