---
output: 
  pdf_document:
    keep_tex: false
    fig_caption: false
subparagraph: yes
geometry: margin=1.5cm
fontsize: 11pt  
header-includes:
   - \usepackage{titlesec}
   - \titlespacing*{\section}{0pt}{0.75\baselineskip}{0.1mm}
   - \usepackage[table]{xcolor}
   - \usepackage{tikz}
   - \usetikzlibrary{positioning,shapes}
   - \usepackage{fancyhdr}
   - \pagestyle{fancy}
   - \fancyhf{}
   - \cfoot{\thepage}
   - \renewcommand{\headrulewidth}{0pt}
   - \chead{\begin{tikzpicture}\fill[blue] (current page.north west) rectangle ([yshift = -1cm]current page.north east);\fill[gold] ([yshift = -1.15cm]current page.north west) rectangle ([yshift = -1cm]current page.north east);\end{tikzpicture}}
   - \hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}
   - \let\oldhref\href
   - \renewcommand{\href}[2]{\oldhref{#1}{\bfseries#2}}

params: 
  draft: FALSE
  pages: 2
  aq_num: ""
---
<!-- 
NOTE: 
\usepackage[table]{xcolor} must be top in the list because otherwise it
clashes with another package (tikz, I believe, but not certain)
-->

```{r, include = FALSE}
# Set some knitr options 
# - We never want to show code, so echo = FALSE
knitr::opts_chunk$set(echo = FALSE)
```

<!-- Document formatting -->

 <!-- Specify sans-serif fonts -->
\renewcommand{\familydefault}{\sfdefault}

<!-- Make tikz pictures relative to the page -->
\tikzset{%
  missing/.style = {minimum width = 0.64\textwidth, minimum height = 0.2\textheight, font = \large},%
  present/.style = {minimum width = 0.64\textwidth},%
  every picture/.style = {remember picture, overlay, inner sep = 0pt, line width=0pt,/utils/exec={\sffamily}}}

<!-- Define colours -->
\definecolor{blue}{HTML}{003D7E}
\definecolor{gold}{HTML}{FCCA06}
\definecolor{grey}{HTML}{505050}

<!-- Make urls bold -->
\def\UrlFont{\bfseries}



\begin{tikzpicture}

  `r  # Top blue bar with title and gold line`
  \fill[blue] (current page.north west) rectangle ([yshift = -3cm]current page.north east);
  \fill[gold] ([yshift = -3cm]current page.north west) rectangle ([yshift = -3.15cm]current page.north east);
  
  `r  # Title`
  \node[below = 1cm of current page.north, white, font = \Huge\bf] (num) {Aquifer Factsheet - Companion Document};
  \node[below = 0.3cm of num, white, font = \large\bf] {Updated `r Sys.Date()`};

\end{tikzpicture}

`r # Add vertical spacing to push text down below header`
\vspace{1.5cm}

The purpose of this companion document is to provide more detailed information related to the terms, analytical methods, and data sources used to produce the Aquifer factsheets.

### *Disclaimer*
\vspace{-4mm}

The information in this Factsheet has been prepared from information currently available to the BC government. As available information is limited in nature, this Factsheet only provides a broad overview of information about the aquifer and is not intended to provide a comprehensive description of the aquifer. The Factsheet is being provided as a public service on an “as is” basis and without any warranty as to the fitness or suitability of the information in it for any particular purpose. The information in this Factsheet has not been tested or verified by the BC government. Consequently, this Factsheet should not be relied upon as providing complete or specific information or advice for use in responding to or assessing particular sites or circumstances.

Persons using this Factsheet should take steps to independently verify the information herein provided. It is your responsibility to review your particular sites or circumstances and then to determine the accuracy, suitability, reliability, usability, completeness, timeliness or applicability of the information in this Factsheet to your particular sites or circumstances. Provision of this information does not substitute for identification and analysis of individual sites or circumstances by a suitably qualified professional.

Persons using this Factsheet do so at their own risk. The BC government accepts no liability or responsibility for the relevancy, suitability, reliability, usability, completeness, timeliness, accuracy or applicability of any of the information in this Factsheet to individual sites or circumstances, nor for any results obtained from its use. Users of this Factsheet are wholly responsible for independently verifying the appropriateness of the information herein provided to their individual sites or circumstances based on their own professional advice.

----

# Aquifer Description (based on Subtype)

The aquifer description is a generic description based on the subtype classification of the aquifer assigned at the time of mapping. A complete list of Aquifer subtype code descriptions can be found on the [BC Government ground water website](https://www2.gov.bc.ca/gov/content/environment/air-land-water/water/groundwater-wells/aquifers/aquifer-subtype-code-description).

<https://www2.gov.bc.ca/gov/content/environment/air-land-water/water/groundwater-wells/aquifers/aquifer-subtype-code-description>

# Water District

British Columbia is divided into named and described water districts. A complete list of the Water Districts is provided in the [Water Sustainability Act](http://www.bclaws.ca/civix/document/id/complete/statreg/38_2016).

<http://www.bclaws.ca/civix/document/id/complete/statreg/38_2016>

# No. of Wells Correlated to Aquifers

The number of wells correlated to an aquifer represents the number of wells that were identified as being completed within the aquifer at the time of mapping. There are several reasons why wells appearing within the aquifer polygon may not be correlated to the aquifer including: a) the well was constructed after the time of mapping, b) no lithological information provided on the well log, or c) the well was completed either below or above the identified aquifer unit.


# Vulnerability, Productivity and Aquifer classification

Values are determined at the time of mapping according to the BC Aquifer Classification system, which are described in [The Guide to using the BC Aquifer Classification Maps – For the Protection and Management of Groundwater](http://www.env.gov.bc.ca/wsd/plan_protect_sustain/groundwater/aquifers/reports/aquifer_maps.pdf). The guide presents a detailed description of the BC Aquifer Classification System, as well as the methodologies employed in classifying the aquifer, and discussions on some of the limitations of the data. This should help the reader to better understand the criteria used to identify, delineate and classify an aquifer. The classification component characterizes the aquifer based on the level of development of the groundwater resource (the water supply available relative to the amount of demand placed on that water supply) at the time of mapping, and also based on the vulnerability of the aquifer to contamination.

<http://www.env.gov.bc.ca/wsd/plan_protect_sustain/groundwater/aquifers/reports/aquifer_maps.pdf>

# Hydraulic Connectivity 

The likelihood of hydraulic connectivity is inferred based on aquifer sub-type. The determination is based on a desktop assessment and has not been field tested or verified. The guidance document [Determining the Likelihood of Hydraulic Connection](http://a100.gov.bc.ca/appsdata/acat/documents/r50832/HydraulicConnectMW3_1474311684426_4310694949.pdf) provides detailed information related to the methodologies and assumptions underlying the assessment.

<http://a100.gov.bc.ca/appsdata/acat/documents/r50832/HydraulicConnectMW3_1474311684426_4310694949.pdf>  

# BC Aquifer Stress Index

The aquifer stress index uses the groundwater footprint and aquifer-scale estimates of withdrawal, recharge and the groundwater contribution to environmental flows. A description of the data sources and the methods and limitations is available on the BC Aquifer Stress index website.

Aquifers are classified as:  

- More stressed (highly certain) if ALL results suggest aquifer stress
- More stressed (less certain) if SOME results suggest aquifer stress
- Less stressed if NONE of the results suggest aquifer stress
- Methods not applicable where data is not available or for confined aquifers

[http://governmentofbc.maps.arcgis.com/home/webmap/viewer.html?  
webmap=6c137fb01a364ee699440a28619e45c2](http://governmentofbc.maps.arcgis.com/home/webmap/viewer.html?webmap=6c137fb01a364ee699440a28619e45c2)

# Reported Well Yield

Reported well yields are based on the estimates recorded by the driller at the time of well construction. It is only an estimate and is not necessarily based on measured values. As defined in [The Guide to using the BC Aquifer Classification Maps – For the Protection and Management of Groundwater](http://www.env.gov.bc.ca/wsd/plan_protect_sustain/groundwater/aquifers/reports/aquifer_maps.pdf), estimated yields are categorize as follows:

- \< 0.3 L/s are considered "Low" yield
- 0.3 - 3.0 L/s are considered "Medium" yield
- \> 3.0 L/s are considered "High" yield

<http://www.env.gov.bc.ca/wsd/plan_protect_sustain/groundwater/aquifers/reports/aquifer_maps.pdf>

# Reported Static Water Depth

Water depth is reported in meters below ground surface and represents the water level measured by the driller at the time of well construction.  


# Reported Well Depth

The well depth is reported in meters below ground surface as measured by the driller at the time of well construction. 

\vspace{5mm}

\begin{minipage}[t]{0.6\textwidth}
  \section{Summary Box Plots for Well Yield, Static Water Depth and Well Depth}
  \vspace{3mm}
  The boxplots provide a summary of the available information for wells correlated to the aquifer.\\
  
  \begin{itemize}
    \item n = the number of wells included in the summary
    \item upper 'hinge' = first quartile
    \item lower 'hinge' = third quartile
    \item crossbar = median
    \item whisker = maximum and minimum values\\(within interquartile range)
    \item points = outliers (defined as 1.5 x interquartile range)
  \end{itemize}
  
  \vspace{0.5cm}
  
  \textbf{Note:} Data not plotted when n < 5
  
  \vspace{0.5cm}
  
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
  \centering
  \textbf{Box Plot Key}\\
  \includegraphics[width = 0.7\textwidth]{../figures/boxplot_key.png}
\end{minipage}


# Water Level Summary and Precipitation Summary Plot

The Water Level Summary Plots are based on data collected through the Provincial Groundwater Observation Well Network. 

<https://catalogue.data.gov.bc.ca/dataset/57c55f10-cf8e-40bb-aae0-2eff311f1685>
  

The dataset comprises daily mean water levels collected from all provincial observation wells. Historically, the water level data was collected at varying frequencies and with measurement frequencies that have changed over the years. To summarize the data, the median values were calculated for any month that has more than one reading. The median and percentile values plotted on the graph were then calculated based on monthly values for all years available. Monthly water level summaries were produced for observation wells with a minimum of 10 years of data. "Preliminary" plots are provided for data sets with between 5 and 10 years of data. The extreme Minimum and Maximum values represent the highest and lowest values ever recorded for a particular month. 

The Precipitation Summary Plots are based on the [Canadian Climate Normals (1981-2010) dataset accessible from the Environment Canada website](http://climate.weather.gc.ca/climate_normals). The nearest climate station at similar elevation to the aquifer (and typically within a maximum distance of 10km) was selected as representative.   

<http://climate.weather.gc.ca/climate_normals>

# Trend Analysis

The trend analysis was conducted by Environmental Reporting BC. A full description of the methods used for the trends analysis are available on the [State of The Environment website](http://www.env.gov.bc.ca/soe/indicators/water/groundwater-levels.html).

<http://www.env.gov.bc.ca/soe/indicators/water/groundwater-levels.html>


# Piper Plot

The chemistry results presented in the Piper plot data were obtained from the Environmental Monitoring System (EMS) web reporting site (<https://a100.gov.bc.ca/pub/ems>) using the R package "rems" (<https://github.com/bcgov/rems/blob/master/README.Rmd>) and converted to a format compatible with the groundwater software program Aquachem (Waterloo Hydrogeologic, 2014). Chemistry results were screened for data quality by assessing the charge balance error. Only samples with a charge balance error of less than 10% were included on the piper plot.

**Reference**  
Waterloo Hydrogeologic (2014). AquaChem Water Quality Analysis & Geochemical Modeling v.2014.2.

<!-- Add draft watermark -->
```{r, results = "asis"}
  if(params$draft) draft_tag()
```

